### 2017-04-10 paper/oopsla17-submission/evaluation-utility-graph.tex
adding recall to utility graph

\begin{figure}[t]
\centering
\begin{subfigure}[t]{\linewidth}
\centering
\begin{tikzpicture}
\begin{axis}[
  % name=slice,
  % scale only axis,
  %at=(feature.above north), anchor=below south east,
  ybar stacked,
  width=0.5\linewidth,
  height=5cm,
  %title={Impact of Type Error Slice},
  ylabel={Accuracy},
  bar width=0.5cm,
  ymin=0.2,
  ymax=1,
  ytick={0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0},
  yticklabel={\pgfmathparse{\tick*100}\pgfmathprintnumber{\pgfmathresult}\,\%},
  ytick style={draw=none},
  ymajorgrids = true,
  symbolic x coords={op+slice-no-slice, op+slice, op+slice-only-slice},
  enlarge x limits=0.25,
  xtick=data,
  xtick style={draw=none},
  xticklabels={\textsc{Local Syntax}, +\InSlice, \textsc{Filter \InSlice}},
  %x tick label style={rotate=45, anchor=north east},
  reverse legend,
  transpose legend,
  legend style={
    %legend pos = outer north east,
    at={(1.5,0.5)},
    anchor=center,
    legend columns=4
  },
]

@@

\addplot[draw=black, fill=green1, bar shift=.25cm] table[x=features, y=top-1] {\SliceHiddenBench};
\addlegendentry{Top-1}
\addplot[draw=black, fill=green2, bar shift=.25cm] table[x=features, y expr=\thisrow{top-2} - \thisrow{top-1}] {\SliceHiddenBench};
\addlegendentry{Top-2}
\addplot[draw=black, fill=green3, bar shift=.25cm] table[x=features, y expr=\thisrow{top-3} - \thisrow{top-2}] {\SliceHiddenBench};
\addlegendentry{Top-3}
\addlegendimage{empty legend}
\addlegendentry{\hiddenFH}

@@

\addplot[draw=black, fill=blue1, bar shift=-.25cm] table[x=features, y=top-1] {\SliceLinearBench};
\addlegendentry{Top-1}
\addplot[draw=black, fill=blue2, bar shift=-.25cm] table[x=features, y expr=\thisrow{top-2} - \thisrow{top-1}] {\SliceLinearBench};
\addlegendentry{Top-2}
\addplot[draw=black, fill=blue3, bar shift=-.25cm] table[x=features, y expr=\thisrow{top-3} - \thisrow{top-2}] {\SliceLinearBench};
\addlegendentry{Top-3}
\addlegendimage{empty legend}
\addlegendentry{\linear}
\end{axis}
\end{tikzpicture}
\caption{Impact of type error slice on blame accuracy.}\label{fig:slice-utility}
\end{subfigure}

@@

\addplot[draw=black, fill=green1, bar shift=.25cm] table[x=features, y=top-1] {\FeatureHiddenBench};
% \addlegendentry{Top-1}
\addplot[draw=black, fill=green2, bar shift=.25cm] table[x=features, y expr=\thisrow{top-2} - \thisrow{top-1}] {\FeatureHiddenBench};
% \addlegendentry{Top-2}
\addplot[draw=black, fill=green3, bar shift=.25cm] table[x=features, y expr=\thisrow{top-3} - \thisrow{top-2}] {\FeatureHiddenBench};
% \addlegendentry{Top-3}
% \addlegendimage{empty legend}
% \addlegendentry{\hiddenFH}

@@

\addplot[draw=black, fill=blue1, bar shift=-.25cm] table[x=features, y=top-1] {\FeatureLinearBench};
% \addlegendentry{Top-1}
\addplot[draw=black, fill=blue2, bar shift=-.25cm] table[x=features, y expr=\thisrow{top-2} - \thisrow{top-1}] {\FeatureLinearBench};
% \addlegendentry{Top-2}
\addplot[draw=black, fill=blue3, bar shift=-.25cm] table[x=features, y expr=\thisrow{top-3} - \thisrow{top-2}] {\FeatureLinearBench};
% \addlegendentry{Top-3}
% \addlegendimage{empty legend}
% \addlegendentry{\linear}

>>>>

\begin{figure}[t]
\centering
\begin{subfigure}[t]{\linewidth}
\centering
\begin{tikzpicture}
\begin{axis}[
  % name=slice,
  % scale only axis,
  %at=(feature.above north), anchor=below south east,
  ybar stacked,
  width=0.5\linewidth,
  height=5cm,
  %title={Impact of Type Error Slice},
  ylabel={Accuracy},
  bar width=0.5cm,
  ymin=0.2,
  ymax=1,
  ytick={0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0},
  yticklabel={\pgfmathparse{\tick*100}\pgfmathprintnumber{\pgfmathresult}\,\%},
  ytick style={draw=none},
  ymajorgrids = true,
  symbolic x coords={op+slice-no-slice, op+slice, op+slice-only-slice},
  enlarge x limits=0.25,
  xtick=data,
  xtick style={draw=none},
  xticklabels={\textsc{Local Syntax}, +\InSlice, \textsc{Filter \InSlice}},
  %x tick label style={rotate=45, anchor=north east},
  reverse legend,
  transpose legend,
  legend style={
    %legend pos = outer north east,
    at={(1.5,0.5)},
    anchor=center,
    legend columns=5
  },
]

@@

\addplot+[stack plots=false, draw=black, fill=none, thick, bar shift=.25cm] table[x=features, y=recall] {\SliceHiddenBench};
\addlegendentry{Recall}
\addplot[draw=black, fill=green1, bar shift=.25cm] table[x=features, y=top-1] {\SliceHiddenBench};
\addlegendentry{Top-1}
\addplot[draw=black, fill=green2, bar shift=.25cm] table[x=features, y expr=\thisrow{top-2} - \thisrow{top-1}] {\SliceHiddenBench};
\addlegendentry{Top-2}
\addplot[draw=black, fill=green3, bar shift=.25cm] table[x=features, y expr=\thisrow{top-3} - \thisrow{top-2}] {\SliceHiddenBench};
\addlegendentry{Top-3}
\addlegendimage{empty legend}
\addlegendentry{\hiddenFH}

@@

\addplot+[stack plots=false, draw=black, fill=none, thick, bar shift=-.25cm] table[x=features, y=recall] {\SliceLinearBench};
\addlegendentry{Recall}
\addplot[draw=black, fill=blue1, bar shift=-.25cm] table[x=features, y=top-1] {\SliceLinearBench};
\addlegendentry{Top-1}
\addplot[draw=black, fill=blue2, bar shift=-.25cm] table[x=features, y expr=\thisrow{top-2} - \thisrow{top-1}] {\SliceLinearBench};
\addlegendentry{Top-2}
\addplot[draw=black, fill=blue3, bar shift=-.25cm] table[x=features, y expr=\thisrow{top-3} - \thisrow{top-2}] {\SliceLinearBench};
\addlegendentry{Top-3}
\addlegendimage{empty legend}
\addlegendentry{\linear}

\end{axis}
\end{tikzpicture}
\caption{Impact of type error slice on blame accuracy.}\label{fig:slice-utility}
\end{subfigure}

@@

\addplot+[stack plots=false, draw=black, fill=none, thick, bar shift=.25cm] table[x=features, y=recall] {\FeatureHiddenBench};
%\addlegendentry{Recall}
\addplot[draw=black, fill=green1, bar shift=.25cm] table[x=features, y=top-1] {\FeatureHiddenBench};
% \addlegendentry{Top-1}
\addplot[draw=black, fill=green2, bar shift=.25cm] table[x=features, y expr=\thisrow{top-2} - \thisrow{top-1}] {\FeatureHiddenBench};
% \addlegendentry{Top-2}
\addplot[draw=black, fill=green3, bar shift=.25cm] table[x=features, y expr=\thisrow{top-3} - \thisrow{top-2}] {\FeatureHiddenBench};
% \addlegendentry{Top-3}
% \addlegendimage{empty legend}
% \addlegendentry{\hiddenFH}

@@

\addplot+[stack plots=false, draw=black, fill=none, thick, bar shift=-.25cm] table[x=features, y=recall] {\FeatureLinearBench};
\addplot[draw=black, fill=blue1, bar shift=-.25cm] table[x=features, y=top-1] {\FeatureLinearBench};
% \addlegendentry{Top-1}
\addplot[draw=black, fill=blue2, bar shift=-.25cm] table[x=features, y expr=\thisrow{top-2} - \thisrow{top-1}] {\FeatureLinearBench};
% \addlegendentry{Top-2}
\addplot[draw=black, fill=blue3, bar shift=-.25cm] table[x=features, y expr=\thisrow{top-3} - \thisrow{top-2}] {\FeatureLinearBench};
% \addlegendentry{Top-3}
% \addlegendimage{empty legend}
% \addlegendentry{\linear}
